### 2014-11-28 Neutral_simulPow.Rmd
Finished results corrected abstract start with discussion

## ADD ANOTHER COLUM WITH MEANSP
require(dplyr)
# DONE! in .RData
#
#pow_ADq10 <- pow_ADq10 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))
#
#
#comp_ADq10 <- comp_ADq10 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
#  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))

plotPow_MeanSp_difR(comp_ADq10)

ggsave("powADq10_DifReplacement.png", width=6,height=6,units="in",dpi=600)

@@

>>>>

require(plyr)
require(dplyr)
# DONE! in .RData
#
#pow_ADq10 <- pow_ADq10 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))
#
#
#comp_ADq10 <- comp_ADq10 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
#  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))

p1 <- plotPow_MeanSp_difR(comp_ADq10)
ggsave("powADq10_DifR_256.png", width=6,height=6,units="in",dpi=600)

p2 <- plotPow_MeanSp_difR(comp_ADq10,512)
ggsave("powADq10_DifR_512.png", width=6,height=6,units="in",dpi=600)

p1 <- rbind(p1,p2)
p1 <- select(p1,Side,spMeta,Type:n) %>% arrange(Side,spMeta,Type,DifR) 
write.table(format(p1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)

rm(p1,p2)

@@

## Simulations to plot spatial patterns with different replacement Rate

```{r neutral_SpSimPlot256, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

# meta = 64, side=250, time=500
sad64 <- simul_NeutralSAD(64,256,500)

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1))
g

setwd("..")
ggsave("spat_NeuLog64_256.png", width=8,height=6,units="in",dpi=600)

# Plot Dq for simulations in txt files (NULL)
#

setwd("Simul")
plotNeutral_Dq(64,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog64_256.png", width=8,height=4,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(8,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog8_256.png", width=8,height=4,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(256,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog256_256.png", width=8,height=4,units="in",dpi=600)

# Plot simulations for all metacommunities 
#
setwd("Simul")
plotNeutral_Dq(0,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog_NumSp_256.png", width=8,height=8,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(0,512,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog_NumSp_512.png", width=8,height=8,units="in",dpi=600)

### Plot Average SAD!
setwd("Simul")
den <- plotNeutral_SAD(0,256)

setwd("..")
ggsave("RAD_NeuLog_spMeta_256.png", width=8,height=6,units="in",dpi=600)

# Create table with R2 of neutral models Dq
#

setwd("Simul")
Dqq <- R2Neutral_Dq(256)
Dqq <- rbind(Dqq,R2Neutral_Dq(512))

Dqq <- arrange(Dqq,DqType,Side,spMeta,ReplacementRate,Freq60,Freq90) %>% select(DqType,Side,spMeta,meanSp,ReplacementRate,Freq60,Freq90)

setwd("..")

#write.table(format(Dqq,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)

require(pander)
pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)

# Table with mean number of species by replacement rate
#
Dqq <- select(Dqq,Side,spMeta,ReplacementRate,meanSp)

#write.table(format(Dqq,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)
pandoc.table(format(Dqq,digits=2),style="grid",split.tables=Inf)

rm(Dqq,Dqq1)
```
